LAGOS lake depth

### 2020-02-06 figures/00_maps.Rmd
clean up bathy map

dt_bathy <- st_sf(dt_bathy, geometry = dt_bathy$geom)

gg_bathy <- 
  ggplot() + 
    geom_sf(data = study_bbox[2,], alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
    geom_sf(data = states_focal, fill = "white", color = "black", size = 0.4) + 
    geom_sf(data = dt_bathy, aes(color = maxdepth_class), 
                    size = 0.3, alpha = 1) +
    scale_color_manual(values = viridisLite::viridis(5)) +
    labs(color = "Max depth (m)") +
    coord_sf(datum =  NA) +
    theme_void()

>>>>

dt_bathy <- st_sf(dt_bathy, geometry = dt_bathy$geom)
dt_bathy <- mutate(dt_bathy, maxdepth_class = droplevels(dt_bathy$maxdepth_class)) 
dt_bathy <- dplyr::filter(dt_bathy, !is.na(maxdepth_class))

gg_bathy <- 
  ggplot() + 
    geom_sf(data = st_as_sfc(st_bbox(dt_bathy)), alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = st_crop(states_all, st_as_sfc(st_bbox(dt_bathy))), fill = "gray", color = "black", size = 0.3) +
    geom_sf(data = st_crop(states_focal, st_as_sfc(st_bbox(dt_bathy))), fill = "white", color = "black", size = 0.4) + 
    geom_sf(data = dt_bathy, aes(color = maxdepth_class), 
                    size = 0.2, alpha = 0.8) +
    scale_color_manual(values = viridisLite::viridis(4)) +
    labs(color = "Max depth (m)") +
    coord_sf(xlim = c(-103.81483, -67.10548), ylim = c(37.5, 48.72102)) +
    theme_void()
